Cole Juracek - Model Building

### 2021-03-14 cjuracek_model_building.Rmd
Small tweaks

```{r}
#model_1 <- lmer(log_ppm ~ (1 | state) + (source + mgstr + bulk_purchase + year)^2, data=streetrx)
model_1 <- lmer(log_ppm ~ (1 | state) + source + mgstr + bulk_purchase + year, data=streetrx)
BIC(model_1)
```

@@

```{r}
model_2 <- lmer(log_ppm ~ (1 | state) + USA_region + source + mgstr + bulk_purchase +
                Primary_Reason + year, data=streetrx)
#BIC(model_2)
step(model_2)
```

>>>>

```{r}
model_1 <- lmer(log_ppm ~ (1 | state) + source + mgstr + bulk_purchase + year, data=streetrx)
BIC(model_1)
```

@@

```{r}
model_2 <- lmer(log_ppm ~ (1 | state) + USA_region + source + mgstr + bulk_purchase +
                Primary_Reason + year, data=streetrx)
step(model_2)
```
